## ̥$$ MDSC-201(P)$$

## $$Assignment-IV$$

**Author : Akula Venkata Satya Sai Gopinadh**

**Date : 27-02-2023**

## Plotting In R Programming

### 1.PIE CHART :

```{r}
a <- c(24,45,78,94,33,11,56)

labels <- c("Kerala","Karantaka","Puttaparthi","Narasaraopet","Guntur",'Banglore',"Muddenahalli")

pie(a,labels)
```

```{r}
cities <- c(Munnar=24,Cooorg=45,Guntur=78,Narasaraopet = 94,Muddenahalli=55)
cities

pct <- round(cities/sum(cities)*100)		# calculate percentages
lbls <- paste(names(cities), pct, "%") 


```

```{r}
pie(cities, main = "City Pie chart", col = c("white","black",'red','blue','skyblue'),labels=lbls)
```

```{r}
x <-  c(21, 62, 10,53)
labels <-  c("London","New York","Singapore","Mumbai")

piepercent<- round(100*x/sum(x), 1)

pie(x, labels = piepercent, main = "City pie chart",col = rainbow(length(x)))
legend("topright", c("London","New York","Singapore","Mumbai"), cex = 0.8,
   fill = rainbow(length(x)))
```

### 2. BAR CHART :

barplot(H,xlab,ylab,main, names.arg,col)

```{r}
S <- c(12,3,4,11,35,7)

barplot(S)
```

```{r}
s <- c(12,2,4,2,0,5,15,53)
m <- c("Match-1","Match-2","Match-3","Match-4","Match-5","Match-6","Match-7","Match-8")

barplot(s,names.arg=m,xlab="Cricket Match", ylab ="Score",col="skyblue",
        main = "Cricket Performance",border ='black')
```

```{r}

```

### Stacked Bar Chart :

```{r}
colors = c("white","black","skyblue")
subjects <- c("101","102","103","104","105")
students <- c("Satya","Sai","Venkat")

Values <- matrix(c(2,9,3,11,9,4,8,7,3,12,5,2,8,10,11), nrow = 3, ncol = 5, byrow = TRUE)

barplot(Values, main = "Academic Performance Subject-Wise", names.arg = subjects, xlab = "Subjects", ylab = "Marks-Secured", col = colors)

legend("topleft",regions=TRUE, cex = 1.3, fill = colors)

```

### 3.BOX PLOT :

boxplot(x,data, notch, varwidth, names, main)̥

```{r}
input <- mtcars[,c('mpg','cyl')]
print(head(input))

```

```{r}
boxplot(mpg ~ cyl, data = mtcars, xlab = "Number of Cylinders",
   ylab = "Miles Per Gallon", main = "Mileage Data")
```

```{r}
boxplot(mpg ~ cyl, data = mtcars, 
   xlab = "Number of Cylinders",
   ylab = "Miles Per Gallon", 
   main = "Mileage Data",
   notch = TRUE, 
   varwidth = TRUE, 
   col = c("lightblue","pink","grey"),
   names = c("High","Medium","Low"))
```

### 4.Histogram:

hist(v,main,xlab,xlim,ylim,breaks,col,border)

```{r}
x<-c(1,22,32,14,5,67,8,9,10)

hist(x,xlab = "Weight",col = "skyblue",border = "black")
```

```{r}
hist(x,xlab = "Weight",col = "white",border = "black", xlim = c(0,80), ylim = c(0,2),
   breaks = 5)
```

### 6.LINE PLOT:

```{r}
y<- c(4,1,7,2,9,3)

plot(y,type='o')

```

```{r}

v <- c(10,8,12,4,2,8,15)

plot(v,type = "o", col = "green", xlab = "Matches", ylab = "Score",
   main = "Cricket Performance")


```

### Multile Lines in a Chart:

```{r}
v <- c(10,8,12,4,2,8,15)
t <- c(14,7,6,9,3)

plot(v,type = "o", col = "green", xlab = "Matches", ylab = "Score",
   main = "Cricket Performance")

lines(t, type = "o", col = "blue")


```

### SCATTER PLOT:

```{r}
input <- mtcars[,c('wt','mpg')]
print(head(input))
```

```{r}

input <- mtcars[,c('wt','mpg')]
# Plot the chart for cars with weight between 1.5 to 4 and mileage between 15 and 30.
plot(x = input$wt,y = input$mpg,
   xlab = "Weight",
   ylab = "Milage",
   xlim = c(1.5,4),
   ylim = c(15,40),		 
   main = "Weight vs Milage"
)
 

```

```{r}
pairs(~wt+mpg+disp+cyl,data = mtcars,
   main = "Scatterplot Matrix")
```

### MEASURES OF CENTRAL TENDENCY (MEAN, MEDIAN , MODE):

### MEAN :

```{r}
x <- c(1.2,-7,30,14.2,8.1,22,24,-2,18,-12)

mean <-mean(x)
paste("MEAN : ",mean)

```

```{r}
x <- c(1.2,-7,30,14.2,NA,8.1,22,24,NA,-2,18,-12,NA)
mean <-  mean(x,na.rm = TRUE)
paste("MEAN after dropping NA values :",mean)
```

### MEDIAN:

```{r}
median <- median(x)
paste("Median :",median)
```

```{r}
x <- c(1.2,-7,30,14.2,NA,8.1,22,24,NA,-2,18,-12,NA)
median <-  median(x,na.rm = TRUE)
paste("MEDIAN after dropping NA values :",median)

```

### MODE:

```{r}
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}


```

```{r}
x <- c(12,2,3,12,3,1,23,4,12,2,5,1,1)
mode <- getmode(x)
paste("MODE of the given vector is :",mode)
```

```{r}


```

```{r}

```

```{r}

```

```{r}

```

### **Finding Mean,Median & Mode using a DATASET:**

```{r}
# lets take a dataset called CardioGoodFitness.csv

myData = read.csv("CardioGoodFitness.csv",
				stringsAsFactors=F)

print(head(myData))

```

```{r}

mean = mean(myData$Age)
paste("MEAN :", mean)
```

```{r}
median = median(myData$Age)
paste("Median : ",median)
```

```{r}
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

mode<- getmode(myData$Age)
paste("Mode of the Age is: ",mode)
```

```{r}

```

```{r}

```

```{r}

```

```{r}
  
```
