# $$ MDSC-201(P) $$

## $$Unit - 2 $$

## Topics :

## 1. Simple Linear Regression.

## 2. Multiple Linear Regression.

## 3. Check MultiCollinearity of the Data.

## 4. Residual Analysis.

## 

### *Author: Akula Venkata Satya Sai Gopinadh*

## SIMPLE LINEAR REGRESSION

```{r}
# y = B0 + B1.x

# B0 and B1 are the coefficients 
# x is the predictor variable
# y is the response variable
```

```{r}
x <- c(151, 174, 138, 186, 128, 136, 179, 163, 152, 131)
y <- c(63, 81, 56, 91, 47, 57, 76, 72, 62, 48)
```

## **lm() Function**

This function creates the relationship model between the predictor and the response variable.

### **Syntax**

The basic syntax for **lm()** function in linear regression is −

lm(formula, data)

Following is the description of the parameters used −

-   **formula** is a symbol presenting the relation between x and y.

-   **data** is the vector on which the formula will be applied.

```{r}

relation <- lm(y~x)

print(relation)
```

```{r}
# getting the summary of the relationship using summary function

print(summary(relation))
```

```{r}
x <- c(151, 174, 138, 186, 128, 136, 179, 163, 152, 131)
y <- c(63, 81, 56, 91, 47, 57, 76, 72, 62, 48)

# Apply the lm() function.
relation <- lm(y~x)

print(summary(relation))
```

```{r}
data(mtcars)
head(mtcars)
```

```{r}
model <- lm(mpg ~ wt, data = mtcars)

```

```{r}
summary(model)
```

```{r}

```

```{r}
library(ggplot2)
library(dplyr)
library(broom)
#library(ggpubr)
```

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(x = "Weight", y = "Miles per gallon") +
  ggtitle("Scatter plot (MPG vs WEIGHT)")
```

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(x = "Weight", y = "Miles per gallon") +
  ggtitle("Scatter plot (MPG vs WEIGHT)") +
  geom_smooth(method = "lm", se = FALSE)
```

## Multiple Linear Regression

```{r}
relation_mlr = lm(mpg ~ cyl + disp + hp + wt, data = mtcars)
```

```{r}
summary(relation_mlr)
```

```{r}
ggplot(mtcars, aes(x = wt, y = disp)) +
    geom_point()+ ggtitle("Scatter plot (WEIGHT vs DISP)")+
    geom_smooth(method = "lm", se = FALSE)
```

```{r}

ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_point() +  ggtitle("Scatter plot (WEIGHT vs MPG)")
  geom_smooth(method = "lm", se = FALSE) +
  geom_line(aes(x = wt, y = predict(model)))
```

```{r}
!install.packages("car")
!install.packages("corrplot")

library(car)
library(corrplot)

vif_values <- vif(model_mlr)
vif_values
```

```{r}
actual = mtcars["mpg"]
df <- data.frame(actual, predicted = predict(model_mlr), residuals = residuals(model_mlr))
df
```

```{r}
# Create a scatter plot of the residuals vs predicted values

ggplot(df, aes(x = predicted, y = residuals)) + geom_point()+
                 xlab("Predicted Values")+
                 ylab("Residuals")+
                 ggtitle("Residual Plot")
```

```{r}
# Create a histogram of the residuals

ggplot(df, aes(x = residuals)) +
  geom_histogram(binwidth = 1) +
  xlab("Residuals") +
  ylab("Frequency") +
  ggtitle("Histogram of Residuals")
```

```{r}
# Create a QQ plot of the residuals

qqnorm(residuals(model_mlr))
qqline(residuals(model_mlr))
```

## Logistic Regression

```{r}
library(dplyr)
library(ggplot2)
```

```{r}
data(mtcars)
head(mtcars)
```

```{r}
# Fit a logistic regression model with vs as the response variable
relation_logit <- glm(vs ~ wt + hp, data = mtcars, family = binomial(link = "logit"))
```

```{r}
 # model summary
summary(relation_logit)
```

```{r}
# Create a sequence of predictor variable values
x_seq <- seq(min(mtcars$wt), max(mtcars$wt), length = 100)
df <- data.frame(wt = x_seq, hp = median(mtcars$hp))
head(df)
```

```{r}
y_prob <- predict(relation_logit, newdata = df, type = "response")
df$y_prob <- y_prob
head(df)
```

```{r}
library(ggplot2)
ggplot(data = mtcars, aes(x = wt, y = vs)) +
  geom_point(aes(color = vs)) +
  geom_line(data = df, aes(x = x_seq, y = y_prob), color = "black") +
  labs(x = "Weight", y = "Probability of V/S") +
  ggtitle("Logistic Regression Curve")
```

## Poisson Regression

### **Syntax**

The basic syntax for **glm()** function in Poisson regression is −

    glm(formula,data,family)

Following is the description of the parameters used in above functions −

-   **formula** is the symbol presenting the relationship between the variables.

-   **data** is the data set giving the values of these variables.

-   **family** is R object to specify the details of the model. It's value is 'Poisson' for Logistic Regression.

\
\

```{r}
input <- warpbreaks
print(head(input))

```

```{r}
output <-glm(formula = breaks ~ wool+tension, data = warpbreaks,
   family = poisson)

```

```{r}
print(summary(output))
```

```{r}
ggplot(output, aes(x = breaks, y = wool)) +
  geom_point() +
  geom_line() +
  labs(x = "breaks", y = "wool")
```

## Confusion Matrix

```{r}
data(iris)
head(iris)
```

``` {)}
```

```{r}
library(ggplot2)
set.seed(123)
trainIndex <- createDataPartition(iris$Species, p = 0.8, list = FALSE)
trainData <- iris[trainIndex,]
testData <- iris[-trainIndex,]
```
